Reading Notes

### 2020-08-13 1summ.tex
more comments from boss meeting
replacing <> with %% comments

\begin{center}
\large{\textbf{<Title>}}
%\large{\textbf{ADVANCEMENT OF ORGANIC PHOTOVOLTAICS THROUGH ARTIFICIAL NEURAL NETWORKS}}
\end{center}
\begin{center}
    Jenny W. Fothergill
\end{center}
\begin{center}
    \textbf{Project Summary}
\end{center}
%\begin{center}
%\emph{Maximum of 1 page}
%\end{center}
% This should be a brief statement of the problem you plan to address.
% It should look something like an abstract.

@@

Already the effects of human-influenced climate change are <hurtng everyone in particular poor and disadvantaged groups>.
Burning fossil fuels for energy is the main contributor to rising $CO_{2}$ levels, and the energy demand is only increasing.
This increase in energy demand along with the need to protect our precious climate makes finding efficient, renewable energy technologies of the utmost importance.
Harvesting the abundant solar energy is a <good solution because it is renewable, non-polluting, sustainable>.
Devices which convert light to electricity, called photovoltaics, were originally made of silicon and required rare elements and careful, clean-room processing.
More recently, organic photovoltaic (OPV) devices have recieved attention for their simple, inexpensive manufacture.
Generally OPV devices are made of a multicompound mixture: usually an electron donor and acceptor which form a mosaic-like structure called a bulk-heterojunction (BHJ).
The compounds and polymers used in OPVs are made of common elements and can be synthesized with relative ease.
And the OPV BHJ can often be assembled using simple techniques like roll-to-roll printing in ambient conditions.
The process for OPV to generate electricity is as follows: 
Sunlight excites an electron, which forms an exciton.
This exciton travels to an acceptor/donor interface and is dissociated into free electron and hole.
Then the free charges travel to an electrode which generates current.
However, in order for OPV devices to be a viable solution, they need to be more efficient.
The efficiency of an OPV device can be improved by changing the chemistry of the electron acceptor and donor compounds, the polymer properties, and tuning the processing conditions of the BHJ.
With so many parameters, quickly this becomes an intractable problem for experiments to solve.
This is where molecular simulation comes in.

@@

IM - Potential to advance knowledge and understanding within own and across different fields
- Activities explore creative, original, or potentially transformative concepts?
A coarse graining pipeline will help make multi-scale simulations more accesible and useable for others. 
This can be useful for screening of potential OPV compounds.

@@

- Mechanism to assess success?
<comparing mobilities, diffraction to experiment>

- How qualified is team?
<talk about what I've done already?>

- Adequate resources to carry out activities?
<talk about our supercomputer allocations?>

@@

BI - Potential to benefit society, contribute to achievement of desired societal outcomes
- Activities explore creative, original, or potentially transformative concepts?
<talk about VOTCA?>
<talk about TRUE simulations and reproducibility in the field>

>>>>

\begin{center}
\large{\textbf{Title}} %%TODO
%\large{\textbf{ADVANCEMENT OF ORGANIC PHOTOVOLTAICS THROUGH ARTIFICIAL NEURAL NETWORKS}}
\end{center}
\begin{center}
    Jenny W. Fothergill
\end{center}
\begin{center}
    \textbf{Project Summary}
\end{center}
%\begin{center}
%\emph{Maximum of 1 page}
%\end{center}
% This should be a brief statement of the problem you plan to address.
% It should look something like an abstract.

@@

Already the effects of human-influenced climate change are %%<hurtng everyone in particular poor and disadvantaged groups>.
Burning fossil fuels for energy is the main contributor to rising $CO_{2}$ levels, and the energy demand is only increasing.
This increase in energy demand along with the need to protect our precious climate makes finding efficient, renewable energy technologies of the utmost importance.
Harvesting the abundant solar energy is a %%<good solution because it is renewable, non-polluting, sustainable>.
Devices which convert light to electricity, called photovoltaics, were originally made of silicon and required rare elements and careful, clean-room processing.
More recently, organic photovoltaic (OPV) devices have recieved attention for their simple, inexpensive manufacture.
Generally OPV devices are made of a multicompound mixture: usually an electron donor and acceptor which form a mosaic-like structure called a bulk-heterojunction (BHJ).
The compounds and polymers used in OPVs are made of common elements and can be synthesized with relative ease.
And the OPV BHJ can often be assembled using simple techniques like roll-to-roll printing in ambient conditions.
The process for OPV to generate electricity is as follows: 
Sunlight excites an electron, which forms an exciton.
This exciton travels to an acceptor/donor interface and is dissociated into free electron and hole.
Then the free charges travel to an electrode which generates current.
However, in order for OPV devices to be a viable solution, they need to be more efficient.
The efficiency of an OPV device can be improved by changing the chemistry of the electron acceptor and donor compounds, the polymer properties, and tuning the processing conditions of the BHJ.
With so many parameters, quickly this becomes an intractable problem for experiments to solve.
This is where molecular simulation comes in.

@@

IM - Potential to advance knowledge and understanding within own and across different fields
- Activities explore creative, original, or potentially transformative concepts?
A coarse graining pipeline will help make multi-scale simulations more accesible and useable for others. 
This can be useful for screening of potential OPV compounds.
what makes a good NFA?

@@

- Mechanism to assess success?
%%<comparing mobilities, diffraction to experiment>

- How qualified is team?
%%<talk about what I've done already?>

- Adequate resources to carry out activities?
%%<talk about our supercomputer allocations?>

@@

BI - Potential to benefit society, contribute to achievement of desired societal outcomes
- Activities explore creative, original, or potentially transformative concepts?
%%<talk about VOTCA?>
%%<talk about TRUE simulations and reproducibility in the field>
